\documentclass[12pt]{article}

% Packages
\usepackage{geometry}        % Adjust margins
\usepackage{graphicx}        % Include graphics
\usepackage{booktabs}        % Professional-quality tables
\usepackage{hyperref}        % Hyperlinks
\usepackage{amsmath}         % Math typesetting
\usepackage{float}           % Improved interface for floating objects

% Page Setup
\geometry{
    a4paper,
    left=25mm,
    right=25mm,
    top=25mm,
    bottom=25mm,
}

% Document
\begin{document}

% Title
\begin{center}
    {\Large \textbf{Stock Initial Research Template}}\\[1.5em]
    \textbf{Company Name}: \underline{CNH Industrial N.V.}\\[0.5em]
    \textbf{Ticker Symbol}: \underline{CNHI}\\[0.5em]
    \textbf{Date}: \today
\end{center}

\vspace{1em}

% 1. Company Overview
\section*{1. Company Overview}
CNH Industrial N.V. is a global leader in the capital goods sector, specializing in agricultural and construction equipment. The company designs, produces, and sells machinery and services for the agricultural and construction industries. Operating through well-known brands such as Case IH, New Holland Agriculture, and CASE Construction Equipment, CNH Industrial serves customers worldwide. The company also provides financial services to support the purchase and lease of its equipment.

% 2. Key Financial Metrics
\section*{2. Key Financial Metrics}
\begin{table}[H]
    \centering
    \begin{tabular}{@{}ll@{}}
        \toprule
        \textbf{Metric}                 & \textbf{Value}                    \\
        \midrule
        Market Capitalization           & \$16 billion                      \\
        Revenue (TTM)                   & \$20 billion                      \\
        Net Income (TTM)                & \$1.5 billion                     \\
        Earnings Per Share (EPS)        & \$1.10                            \\
        Price-to-Earnings (P/E) Ratio   & 14                                \\
        Price-to-Book (P/B) Ratio       & 2                                 \\
        Return on Equity (ROE)          & 14\%                              \\
        Debt-to-Equity Ratio            & 0.8                               \\
        Current Ratio                   & 1.3                               \\
        Dividend Yield                  & 2\%                               \\
        \bottomrule
    \end{tabular}
    \caption{Key Financial Metrics}
\end{table}

% 3. Investment Thesis Summary
\section*{3. Investment Thesis Summary}
CNH Industrial is strategically positioned to benefit from global trends in agriculture and infrastructure development. The increasing global population drives demand for agricultural machinery to boost food production. The company's investment in innovation, including automation and alternative propulsion technologies, offers a competitive edge. CNH Industrial's diversified portfolio and global presence reduce reliance on any single market, providing resilience against regional economic fluctuations.

they have good dividend and share repurchase outlook looks pretty bad for 2024 and 2025. 25 percent down still possible but 2x when cycle reverts. we don't know how long the cycle will be, 10 percent likely over the cycle but can be risky. No real competitve advantage.

% 4. Potential Risks and Problems
\section*{4. Potential Risks and Problems}
The company's performance is closely tied to cyclical industries that are sensitive to commodity price fluctuations. A downturn in the agricultural sector can lead to decreased equipment demand. CNH Industrial faces stiff competition from major players like Deere \& Company, which may impact market share and pricing power. Supply chain disruptions and increased raw material costs can adversely affect profitability. Additionally, exposure to emerging markets introduces currency and political risks.

% 5. Valuation Snapshot
\section*{5. Valuation Snapshot}
CNH Industrial's valuation metrics suggest it is reasonably priced relative to industry peers. The P/E ratio aligns with the sector average, indicating the stock is fairly valued based on current earnings, the stock is in a downturn due to the cyclical industry it is in. The company's P/B ratio reflects a moderate valuation of its assets. Considering the cyclical nature of its business, investors should assess the stock's valuation in the context of the industry cycle stage.

% 6. Conclusion
\section*{6. Conclusion}
Based on the initial research, CNH Industrial could merit further detailed analysis. Its strong market position, focus on innovation, and potential to capitalize on global agricultural cycle make it an attractive candidate for investment consideration. However, it is still risky as I see no real competitive advantage and a possible pronlonged down turn of the food cycle, if the share price goes lower this might be more interesting it's a maybe.

% Optional: Additional Notes
\section*{Additional Notes}
Recent insights from prominent investors, such as David Einhorn, highlight the undervalued potential in the agricultural sector. Understanding the cyclical dynamics, as emphasized by investment experts like Peter Lynch, is crucial. The company's proactive approach to share repurchases and dividend policies indicates a commitment to shareholder value.


\end{document}
